\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-07 paper/main.tex
mehtods

\subsection{Datasets}
The data for the different parts of this model were obtained from
various sources. Starting with the protein-protein interactions, we
fetched $\approx 11000$\todo{precise number} human proteins with over 170.000 links from
STRING \citep{STRINGv10}. For the drug-target interactions themselves,
we fetched 137.000 links from STITCH database \citep{STITCHv5}. As
both STRING and STITCH provide probability scores for each
association, we filtered them as advised by a threshold of 700, thus
only obtaining likely interactions.

For the ontology segment we utilized PhenomeNET \citep{PhenomeNET2011}, a collection of various ontologies such as Human Phenotype Ontology \citep{HPO2018}, Gene Ontology (\citet{GOoriginal2000} \citet{GOrecent2020}), Mammalian Phenotype Ontology \citep{MP2009} and numerous others. \todo{which ontologies to cite}
Side effects and their links to drugs were obtained Side Effect Resource (SIDER)\citep{SIDER} and structured according MedDRA database \citep{MedDRA}. They were mapped to PhenomeNET with aid of \textit{Phenomebrowser.net}, which provides a SPARQL query endpoint for the mentioned resources. \\

>>>>

\subsection{Datasets}
We obtain a dataset consisting of $\approx 11000$\todo{precise number}
human proteins with over 170.000\todo{exact number} links from STRING
\citep{STRINGv10}. For the drug-target interactions, we
fetched 137,000\todo{precise}} links from the STITCH database
\citep{STITCHv5}. As both STRING and STITCH provide confidence scores
for each association, we filtered them as advised by a threshold of
$700$, therefore retaining only high-confidence interactions.

We utilize the PhenomeNET ontology \citep{PhenomeNET2011}, an ontology
integrating ontologies such as the Human Phenotype Ontology
\citep{HPO2018}, Gene Ontology \cite{GOoriginal2000, GOrecent2020},
Mammalian Phenotype Ontology \citep{MP2009} and several others.
We obtained side effects and their links to drugs from SIDER
\citep{SIDER}; SIDER contains side effects encoded using identifiers
from the MedDRA database \citep{MedDRA}. We mapped side effects to the
PhenomeNET ontology using the \textit{Phenomebrowser.net}, which
provides a SPARQL query endpoint for the mentioned resources.
